\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass[journal,12pt,twocolumn]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
\usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}                                            
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{problem}{Problem}
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{example}{Example}[section]
\newtheorem{definition}[problem]{Definition}
\newcommand{\BEQA}{\begin{eqnarray}}
\newcommand{\EEQA}{\end{eqnarray}}
\newcommand{\define}{\stackrel{\triangle}{=}}
\theoremstyle{remark}
\newtheorem{rem}{Remark}
\usepackage{circuitikz}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{ASSIGNMENT-1}
\author{EE24BTECH11032- JOHN BOBBY}
\maketitle
\newpage
\bigskip

\begin{enumerate}
	\item Let A and B be two distinct points on the parabola $y^2=4x$. If
the axis of the parabola touches a circle of radius r having
		$AB$ as diameter, then the slope of the line joining A and B
 can be \\
		\hfill\brak{2010}
		\\
		\begin{enumerate}
			\item$\frac{-1}{r}$
			\item$\frac{1}{r}$
			\item$\frac{2}{r}$
			\item$\frac{2}{r}$
		\end{enumerate}
	\item Let the eccentricity of the hyperbola $\frac{x^2}{a^2}-\frac{y^2}{b^2}=1$ be reciprocal to that of the elipse $x^2+4y^2=4$. If the hyperbola
	passes through a focus of the elipse, then \\
		\hfill\brak{2011}
		\\
		\begin{enumerate}
			\item the equation of the hyperbola is $\frac{x^2}{3}-\frac{y^2}{2}=1$
			\item a focus of the hypebola is $(2,0)$
			\item the eccentricity of the hyperbola is $\sqrt{\frac{5}{3}}$
			\item the equation of the hyperbola is $x^2-3y^2=3$
		\end{enumerate}
	\item Let L be a normal to the parabola $y^2=4x$. If L passes through the point $(9,6)$, then the L is given by \\
		\hfill\brak{2010}
		\\
		\begin{enumerate}
			\item $y-x+3=0$
			\item $y+3x-33=0$
			\item $y+x-15=0$
			\item $y-2x+12=0$
		\end{enumerate}
	\item Tangents are drawn to the hyperbola $\frac{x^2}{9}-\frac{y^2}{4}=1$, parallel to the straight line $2x-y=1$.The points of contact of the tangents to the hyperbola
		are \\
		\hfill\brak{2012}
		\\
		\begin{enumerate}
			\item $\brak{\frac{9}{2\sqrt{2}},\frac{1}{\sqrt{2}}}$ 
			\item $ \brak{\frac{-9}{2\sqrt{2}},\frac{-1}{\sqrt{2}}}$
			\item $\brak{3\sqrt{3},-2\sqrt{2}}$
			\item $ \brak{-3\sqrt{3},2\sqrt{2}}$
		
		\end{enumerate}

	\item Let P and Q be distinct points on the parabola $y^2=2x$ such 
		that a circle with PQ as diameter passes through the vertex
		O of the parabola. If P lies in the first quadrant and the area
		of the triangle  \(\Delta \)OPQ is 3$\sqrt{2}$, then which of the following is
		(are) the coordinates of P? \\ 
		\hfill\brak{JEE ADV.2015}
		\\
		\begin{enumerate}
			\item $ \brak{4,2\sqrt{2}}$
			\item $\brak{9,3\sqrt{2}}$
			\item $ \brak{\frac{1}{4},\frac{1}{\sqrt{2}}}$
			\item  $ \brak{1,\sqrt{2}}$
		\end{enumerate}
	\item Let $ E_1$  and $ E_2$ be two elipses whose centres are at the orgin.
              The major axes of $E_1$ and $ E_2$ lie along the x-axis and the
              y-axis,respectively. Let S be the circle $x^2+(y-1)^2=2$.The
		straight line $x+y=3$ touches the curves S, $E_1$ and $E_2$ at P, Q
		and R respectively.Suppose that PQ$=$PR=$\frac{2\sqrt{2}}{3}$. If $e_1$ and
              $e_2$ are the eccentricities of $E_1$ and $E_2$,respectively, then the 
              correct expression(s) is (are) \\
		\hfill\brak{JEE ADV.2015}
		\\
		\begin{enumerate}
			\item $e_1^2+e_2^2=\frac{43}{40}$
			\item $e_1e_2=\frac{\sqrt{7}}{2\sqrt{10}}$
			\item $\abs{ e_1^2-e_2^2}=\frac{5}{8}$
			\item $e_1e_2=\frac{\sqrt{3}}{4}$ 
		\end{enumerate}
	\item Consider the hyperbola H:$x^2-y^2=1$ and a circle S with 
		centre $\vec{N}(x_2,0)$. Suppose that H and S touch each other at a 
	      point $\vec{P}$$(x_1,y_1)$ with $x_1>0$ and $y_1>0$. The common tangent to H and S at P intersects the x-axis at point M. If ${(l,m)}$ is the centroid of the triangle PMN, then correct expressions(s) is(are) \\
	      \hfill\brak{JEE ADV.2015}
	      \\
	      \begin{enumerate}
		      \item $\frac{dl}{dx_1}=1-\frac{1}{3x^2}$ for $x_1>1$ 
		      \item $\frac{dm}{dx_1}=\frac{x_1}{3\sqrt{x_1^2-1}}$ for $x_1>1$ 
		      \item $\frac{dl}{dx_1}=1+\frac{1}{3x^2}$ for $x_1>1$
		      \item $\frac{dm}{dy_1}=\frac{1}{3}$ for $y_1>0$ 
	      \end{enumerate}
      \item The circle $C_1$:$x^2+y^2=3$, with centre at O, intersects the parabola $x^2=2y$ at the point P in the first quadrant. Let the tangent to the circle $C_1$, at P touches other two circles $C_2$ and $C_3$ at $R_2$ and $R_3$, respectively. Suppose $C_2$ and $C_3$ have equal radii $2\sqrt{3}$ and the centres $Q_2$ and $Q_3$,respectively. If $Q_2$ and $Q_3$ lie on the y-axis, then \\ 
	      \hfill\brak{JEE ADV.2016}
	      \\
	      \begin{enumerate}
		      \item $Q_2Q_3=12$
		      \item $R_2R_3=4\sqrt{6}$
		      \item area of the triangle $OR_2R_3$ is $6\sqrt{2}$
		      \item area of the triangle $PQ_2Q_3$ is $4\sqrt{2}$
	      \end{enumerate}
      \item Let P be the point on the parabola $y^2=4x$ which is at the shortest distance from the center S of the circle $x^2+y^2-4x-16y+64=0$. Let Q be the point on the circle
	      dividing the line segment SP internally. Then \\
	      \hfill\brak{JEE ADV.2016}
	      \\
	      \begin{enumerate}
		      \item SP=2$\sqrt{5}$
		      \item SQ:QP=$(\sqrt{5}+1):2$
		      \item the x-intercept of the normal to the parabola at P is 6.
		      \item the slope of the tangent to the circle at Q is $\frac{1}{2}$
		      
	      \end{enumerate}
      \item If $2x-y+1=0$ is a tangent to the hyperbola $\frac{x^2}{a^2}-\frac{y^2}{16}=1$ then which of the following cannot be sides of a right angled triangle? \\
	      \hfill\brak{JEE ADV.2017}
	      \\
	      \begin{enumerate}
		      \item $a,4,1$
		      \item $a,4,2$
		      \item $2a,8,1$
		      \item $2a,4,1$
	      \end{enumerate}
      \item If a chord, which is not tangent, of the parabola $y^2=16x$ has equation $2x+y=p$, and midpoint $(h,k)$, then which of the following is(are) possible value(s) of p,h and k? \\
	      \hfill\brak{JEE ADV.2017}
	      \\
	      \begin{enumerate}
		      \item $p=-2,h=2,k=-4$
		      \item $p=-1,h=1,k=3$
		      \item $p=2,h=3,k=-4$
		      \item $p=5,h=4,k=-3$


	      \end{enumerate}
      \item Consider two straight lines, each of which is tangent to both the circle $x^2+y^2=\frac{1}{2}$
	      and the parabola $y^2=4x$. Let these lines intersect at the point Q. Consider the elipse whose center is at orgin $\vec{O}(0,0)$ and whose semi-major axis is OQ.
	      If the length of the minor axis of the elipse is $\sqrt{2}$, then which of the following statement(s) is(are) TRUE? \\
	      \hfill\brak{JEE ADV.2018}
	      \\
	      \begin{enumerate}
		      \item For the elipse, the eccentricity is $\frac{1}{\sqrt{2}}$ and the length of the latus rectum is 1

		      \item For the elipse, the eccentricity is $\frac{1}{2}$ and the length of the latus rectum is$\frac{1}{2}$
		      \item The area of the region bounded by the elipse between the lines $x=\frac{1}{\sqrt{2}}$ and $x=1$ is $\frac{1}{4\sqrt{2}}(\pi-2)$
		      \item The area of the region bounded by the elipse between the line $x=\frac{1}{\sqrt{2}}$ and $x=1$ is $\frac{1}{16}(\pi-2)$
	      \end{enumerate}

\end{enumerate}
\begin{enumerate}
		\section{SECTION -E SUBJECTIVE PROBLEMS}
	\item Suppose that the normals drawn at three different points on the parabola $y^2=4x$ pass through the point$(h,k)$. Show that $h>2$.\\
		\hfill\brak{1981-4 Marks}
		\\
	\item A is a point on the parabola $y^2=4ax$.The normal at A cuts the parabola again at point B. If AB subtends a right angle at the vertex of the parabola.find the slope of AB. \\
		\hfill\brak{1982-4 Marks}
		\\
      \item Three normals are drawn from the point $(c,0)$ to the curve $y^2=x$. Show that c must be greater than $\frac{1}{2}$. One normal is always the x-axis. Find c for which the other two normals are perpendicular to each other. \\
	      \hfill\brak{1991-4 Marks}
		\\
	\item Through the vertex O of parabola $y^2=4x$,chords OP and OQ are drawn at right angles to one another. Show that for all positions of P, PQ cuts the axis of the parabola at a fixed point. Also find the locus of the middle point of PQ. \\
		\hfill\brak{1994-4 Marks}
		\\
      \item Show that the locus of a point that divides a chord of slope 2 of the parabola $y^2=4x$ internally in the ratio 1:2 is a parabola. Find the vertex of this parabola. \\
	      \hfill\brak{1995-5 Marks}


\end{enumerate}
\end{document}



